article title

### 2022-08-09 article.tex
Moved "list of" to after table of contents
Refactor location of lists, remove several newpage

@@

\newpage
\section{Bold, italics, and underline}\label{sec:bold_italics_underline}
Some of the \textbf{greatest} \textit{discoveries} in \underline{science} were made by \textbf{\textit{accident}}.

\section{URLs}\label{sec:urls}
Hyperlinks within the document can be easily added. For example, \hyperref[sec:graphics]{see Graphics} and \hyperref[fig:anatomy_of_a_matplotlib_figure]{Anatomy of a matplotlib figure} and \hyperref[def:limit]{Definition of a limit}.

Hyperlinks to external URLs can be easily added. For example, see \href{https://en.wikipedia.org/wiki/Latex}{Wikipedia \LaTeX}.
\section{Lists}\label{sec:lists}
\subsection{Unordered list}\label{sec:unordered_list}
\begin{itemize}
    \item Illinois
        \begin{itemize} \item Chicago \item Naperville \end{itemize}
    \item Kentucky
        \begin{itemize} \item Lexington \item Louisville \end{itemize}
\end{itemize}

@@

\newpage
\section{Graphics}\label{sec:graphics}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

@@

\newpage
\section{Tables}\label{sec:tables}

@@

\newpage
\section{Mathematics}\label{sec:mathematics}

@@

\newpage
\section{Greek letters}\label{sec:greek_letters}

@@

\newpage
\section{Theorems}\label{sec:theorems}

@@

\section{Definitions}\label{sec:definitions}

@@

\section{Corollaries}\label{sec:corollaries}
\begin{corollary}
If $f$ is continuous on the interval $[a,b]$, then \[\int_a^b f(x)dx=F(b)-F(a)\] where $F$ is any antiderivative of $f$.
\end{corollary}
\mycorollaries{f is continuous}

\newpage
\section{Lemmas}\label{sec:lemmas}
\begin{lemma}
$x+y=z$
\end{lemma}
\mylemmas{Lem 1}

@@

\begin{lemma}
$q=r$
\end{lemma}
\mylemmas{Lem 3}

\begin{lemma}
$x+y=z$
\end{lemma}
\mylemmas{Lem 4}

\begin{lemma}
$z-r+t=3$
\end{lemma}
\mylemmas{Lem 5}

\begin{lemma}
$q=r$
\end{lemma}
\mylemmas{Lem 6}

\newpage
\section{Propositions}\label{sec:propositions}
\begin{proposition}
$x+y=z$
\end{proposition}
\mypropositions{Prop 1}

@@

\newpage
\section{Citations}\label{sec:citations}

@@

\newpage
\section{Glossary terms}\label{sec:glossary_terms}

@@

\newpage
\listoftables

\newpage
\listofmyequations

\newpage
\listofmytheorems

\newpage
\listofmydefinitions

\newpage
\listofmycorollaries

>>>>

\listoftables

\listofmyequations

\listofmytheorems

\listofmydefinitions

\listofmycorollaries

@@

\section{Creating bold, italics, and underline}\label{sec:bold_italics_underline}
Some of the \textbf{greatest} \textit{discoveries} in \underline{science} were made by \textbf{\textit{accident}}.

\section{Creating URLs}\label{sec:urls}
Hyperlinks within the document can be easily added. For example, \hyperref[sec:graphics]{see Graphics} and \hyperref[fig:anatomy_of_a_matplotlib_figure]{Anatomy of a matplotlib figure} and \hyperref[def:limit]{Definition of a limit}.

Hyperlinks to external URLs can be easily added. For example, see \href{https://en.wikipedia.org/wiki/Latex}{Wikipedia \LaTeX}.

\newpage
\section{Creating lists}\label{sec:lists}
\subsection{Unordered list}\label{sec:unordered_list}
\begin{itemize}
    \item Illinois
        \begin{itemize} \item Chicago \item Naperville \end{itemize}
    \item Kentucky
        \begin{itemize} \item Lexington \item Louisville \end{itemize}
\end{itemize}

@@

\newpage
\section{Inserting graphics}\label{sec:graphics}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

@@

\newpage
\section{Creating tables}\label{sec:tables}

@@

\newpage
\section{Creating mathematics}\label{sec:mathematics}

@@

\newpage
\section{Creating greek letters}\label{sec:greek_letters}

@@

\newpage
\section{Creating theorems}\label{sec:theorems}

@@

\section{Creating definitions}\label{sec:definitions}

@@

\section{Creating corollaries}\label{sec:corollaries}
\begin{corollary}
If $f$ is continuous on the interval $[a,b]$, then \[\int_a^b f(x)dx=F(b)-F(a)\] where $F$ is any antiderivative of $f$.
\end{corollary}
\mycorollaries{f is continuous}

\section{Creating lemmas}\label{sec:lemmas}
\begin{lemma}
$x+y=z$
\end{lemma}
\mylemmas{Lem 1}

@@

\section{Creating propositions}\label{sec:propositions}
\begin{proposition}
$x+y=z$
\end{proposition}
\mypropositions{Prop 1}

@@

\newpage
\section{Inserting citations}\label{sec:citations}

@@

\section{Inserting glossary terms}\label{sec:glossary_terms}

@@
